R Notebook

### 2020-11-25 FEM_R/model_analysis.Rmd
Added call to require(data.table) so the CV2 visualisations would work

require(tidyverse)
require(formattable)
require(reactable)
require(haven)
#require(reshape2)
#require(ggplot2)
#require(gridExtra)

@@

  res <- reactable(t,
            defaultColDef = colDef(
              header = function(value) gsub('_', ' ', value, fixed=TRUE),
              cell = function(value) format(value, nsmall = 2),
              align='center',
              style = function(value) {

              }
              #headerStyle = list(background = "#f7f7f8")
            ),
            columns = list(
              Variable = colDef(
                  minWidth = 160,
                  style = stickyStyle,
                  headerStyle = stickyStyle),
              P_Value_3 = pValColDef,
              P_Value_4 = pValColDef,
              P_Value_5 = pValColDef,
              P_Value_6 = pValColDef,
              P_Value_7 = pValColDef,
              P_Value_8 = pValColDef
            ),
            bordered = TRUE,
            highlight = TRUE,
            striped = TRUE)

>>>>

require(tidyverse)
require(formattable)
require(reactable)
require(haven)
require(data.table)
#require(reshape2)
#require(ggplot2)
#require(gridExtra)

@@

  pValColDef2 <- colDef(
    style = function(value) {
      if (value >= 0.05) {
        color <- "#4ca64c"
      }
      if (value < 0.05) {
        color <- "#ff6666"
      }
      list(background = color)
    },
    minWidth = 110
  )

  res <- reactable(t,
            defaultColDef = colDef(
              header = function(value) gsub('_', ' ', value, fixed=TRUE),
              cell = function(value) format(value, nsmall = 2),
              align = 'center'
            ),
            columns = list(
              Variable = colDef(
                  minWidth = 160,
                  style = stickyStyle,
                  headerStyle = stickyStyle),
              P_Value_3 = pValColDef2,
              P_Value_4 = pValColDef2,
              P_Value_5 = pValColDef2,
              P_Value_6 = pValColDef2,
              P_Value_7 = pValColDef2,
              P_Value_8 = pValColDef2
            ),
            bordered = TRUE,
            highlight = TRUE,
            striped = TRUE)
